\section{Experience}

\cventry
    {Jan 2023 -- Present}
    {Entrepreneur}
    {SEM Trans}
    {Sacramento, CA}
    {}
    {%
        \begin{itemize}
            \item Established and led a freight dispatch service, growing
            the business from inception to profitability.
            \item Innovated an automated invoicing system, reducing manual
            errors and speeding up billing processes.
        \end{itemize}
    }

\cventry
    {Feb 2023 -- Present}
    {Software Engineering Consultant}
    {Freelance and Open Source}
    {Remote}
    {}
    {%
        \begin{itemize}
            \item Conducted comprehensive code reviews, enhancing code
            quality and performance across multiple projects.
            \item Implemented best practices in software development,
            improving project outcomes and client satisfaction.
        \end{itemize}
    }

\cventry
    {Nov 2021 -- Feb 2023}
    {Software Engineer}
    {XPEL One}
    {Sacramento, CA}
    {}
    {%
        \begin{itemize}
            \item Conducted thorough automated and manual testing,
            optimizing databases and ensuring data integrity.
            \item Mentored team, bridging technical and non-technical
            stakeholders for clear communication and project success.
        \end{itemize}
    }

\cventry
    {Mar 2019 -- Nov 2021}
    {Software Engineer}
    {IncoFort}
    {Sacramento, CA}
    {}
    {%
        \begin{itemize}
            \item Developed detailed process flow diagrams, improving
            understanding and communication of system workflows.
            \item Automated complex tasks, reducing manual effort and
            increasing operational efficiency.
        \end{itemize}
    }

\cventry
    {Jan 2019 -- May 2019}
    {Embedded Systems Engineer Intern}
    {American River College}
    {Sacramento, CA}
    {}
    {%
        \begin{itemize}
            \item Designed and simulated circuit boards using CAD software,
            contributing to successful project outcomes.
            \item Gained hands-on experience in embedded systems design and
            troubleshooting, enhancing technical skills.
        \end{itemize}
    }