\underline{Additional Duties}
\begin{enumerate}[ 
    ref = \SecondLevelEnumerator
]
    \item The Contractor shall be solely responsible for any and all
    pre-trip and post-trip inspections of the Equipment.

    \item When under dispatch, the Contractor shall place a check-in call
    to the Carrier every day between the hours of 8:00 am and 10:00 am
    Pacific Standard Time, unless otherwise specified in written form. The
    Contractor will be subject to an administrative fine of up to two
    hundred dollars (\$200.00) for each instance in which this provision is
    violated.
    
    \item The Contractor shall not, under any circumstances, abandon the
    Equipment and/or cargo subject to this Agreement while under the
    Carrier's dispatch.

    \item The Contractor shall keep their phone turned on at all times
    during the operation of the Equipment while under the Carrier's
    dispatch.

    \item The Contractor shall properly determine the condition of the
    freight at the time such freight is picked up from the shipper. The
    Contractor shall inspect all shipments at the time of pick-up, verify
    each item of the freight (i.e., count pallets, pieces, boxes) against
    the bill of lading to ensure that all items are accounted for, and
    ensure that the receiver marks any exceptions or conditions on the bill
    of lading. The Contractor shall immediately report any and all
    shortages, pilferage, spoilage, damage, or any other discrepancies of
    the cargo to the Carrier before pick-up is confirmed.

    \item The Contractor has a duty to transport each shipment to its
    destination in nearly the same condition as when it was picked up.

    \item The Contractor agrees to provide the Carrier with written notice,
    one (1) week in advance, of its decision to place any Equipment subject
    to this agreement out of operation for a period longer than two (2)
    weeks.
    
    \item In the event the Contractor receives instructions regarding the
    transportation of cargo subject to this Agreement from a broker that
    are inconsistent with instructions received from the Carrier's
    dispatch, the Contractor shall follow the directions given by the
    Carrier's dispatch.
\end{enumerate}