\underline{Independent Contractor}
\begin{enumerate}[
    ref = \SecondLevelEnumerator
]
    \item The parties intend to create by this Agreement only the
    relationship of Carrier and Independent Contractor, and not an Employer
    and Employee relationship. Nothing in this Agreement is intended to,
    nor shall be deemed to, affect the status of the Contractor as an
    independent contractor hereunder.

    \item The Contractor shall determine the method, means, and manner of
    performing this Agreement and shall be responsible to the Carrier for
    the performance of this Agreement in accordance with the rules and
    regulations of appropriate regulatory agencies. The Carrier shall
    comply with all such rules and regulations, but the Carrier shall not
    have the right to and will not control the manner or prescribe the
    method of doing that portion of the operations which is contracted for
    in this Agreement, except such control as can reasonably be construed
    to be required by said rules and regulations.

    \item The Carrier has no obligation to pay or withhold state or federal
    employee taxes, or to provide workers' compensation, unemployment
    insurance, or occupational accidents and disability insurance for the
    Contractor or employees, agents, or independent contractors of the
    Contractor. The Contractor agrees to pay all applicable self-employment
    taxes.

    \item The Contractor shall have the right to reject any load assignment
    and has the right and responsibility to choose the route of travel and
    at what point drivers shall take rest stops and refuel the equipment.

    \item The parties are not the agents of each other, and neither party
    shall have the right to bind the other by contract or otherwise, except
    as herein specifically provided. The Contractor shall not charge or
    obtain any article of property or other thing of value on credit,
    either directly or indirectly, to the Carrier, nor in any manner
    attempt to do so.
\end{enumerate}