{
    \subimport{.}{footnotes.tex}

    \underline{Contractor's Personnel}
    \begin{enumerate}[
        ref = \SecondLevelEnumerator
    ]
        \item Contractor agrees to furnish drivers and all other necessary
        labor to perform all of the work Carrier provides for in its rate
        schedules and contracts necessary for:
        \begin{enumerate}[
            ref = \ThirdLevelEnumerator
        ]
            \item The transportation of such commodities
            
            \item The loading and unloading of such commodities
        \end{enumerate}

        \item Contractor certifies, represents, and warrants that all
        driver personnel furnished by Contractor and covered by this
        Agreement will meet and satisfy the driver qualifications of the
        DOT, the appropriate states, and those of Carrier based thereon and
        related thereto. This includes all applicable drug and alcohol
        regulations, and warrants cooperation with all testing procedures.
        Only such qualified personnel may operate the Equipment leased to
        Carrier by the Contractor under this Agreement. The Contractor
        shall furnish to Carrier proof of such qualifications as Carrier
        may reasonably require.

        \item Contractor agrees that Contractor and Contractor's drivers,
        personnel, and agents will not place in or on, or carry onto the
        Equipment, any alcohol, narcotics, illegal drugs, controlled
        substances, explosives, firearms, contraband, or unauthorized
        commodities or hazardous materials. Any violation of this provision
        shall permit Carrier to terminate this Agreement immediately
        without notice. If a violation of this provision subjects Carrier
        to any expenditures or sanctions, Contractor agrees to reimburse
        Carrier for the same.

        \item The Contractor and all personnel furnished or used by the
        Contractor, including drivers, driver's helpers, and laborers, are
        the employees, agents, or independent contractors of the Contractor
        and not of Carrier and as such, Contractor is solely responsible
        for:
        \begin{enumerate}[
            ref = \ThirdLevelEnumerator
        ]
            \item The employee deductions, as may be required by
            governmental agencies.
            
            \item Self-employment taxes, withholding taxes, FICA taxes,
            unemployment compensation taxes, and any other related taxes
            and obligations.

            \item Provision of workers' compensation insurance and
            occupational accident and disability insurance for all
            personnel and drivers provided by the Contractor, including
            those qualified to operate the Equipment.

            \item The Contractor's management of their employees, agents,
            and independent contractors, including recruitment, dismissal,
            supervision, direction, training, wage setting, work hours and
            conditions, and handling of grievances.

            \item Training the Contractor's employees, agents, and
            independent contractors on the Carrier's policies,
            requirements, and the terms of this Agreement.

            \item All costs associated with commercial driver physical
            qualification tests as required under
            49 CFR {\S\S} 391.41 -- 391.49
            \footnote{\PhysicalQualificationsAndExaminationsFootnote},
            and any other qualification testing conducted by the Contractor.

            \item All operating costs and expenses incurred by the
            Contractor's employees, agents, and independent contractors
            while operating the Equipment under this Agreement.
        \end{enumerate}

        \item The driver or drivers of the Equipment shall be exclusively
        the Contractor and/or the employees, agents, or independent
        contractors of the Contractor. The Contractor, and only the
        Contractor, shall be the employer of himself or herself and such
        additional drivers within the meaning of the Internal Revenue Code
        {\S} 3401(d). The Carrier shall have no control over any funds it
        pays to the Contractor, and such funds shall not be considered
        wages within the meaning of {\S} 3401(a) of the Internal Revenue
        Code.

        \item The Contractor agrees to indemnify, defend, and hold harmless
        the Carrier, its parent companies, their directors, employees, and
        agents from any liability, claims, damages, losses, or expenses of
        others, including reasonable attorney fees, arising from or in any
        manner connected with, whether under industrial accident laws,
        workers' compensation laws, or any other state, federal, or common
        law or precedent applicable to the relationship between employers
        and employees.

        \item No passengers are permitted in the Equipment without the
        prior written approval of each passenger by both the Contractor and
        the Carrier.
    \end{enumerate}
}