\section{Terms and Termination}
{
    \setlength{\parskip}{\baselineskip}
    \setlength{\parindent}{0pt}

    This Agreement is effective as of the date hereof and shall continue in
    effect for a period of thirty (30) days from the date hereof.
    Thereafter, it will automatically renew for consecutive thirty (30) day
    periods unless earlier canceled as follows. This Agreement may be
    canceled, with or without cause, by either party at any time by written
    notice to the other. However, the Contractor may not terminate this
    Agreement until the Contractor has completed any unfinished trip the
    Contractor has undertaken at the time, unless authorized to do so by
    the Carrier.

    Upon termination of this Agreement, final settlement will occur within
    forty-five (45) days after the Contractor fulfills the Contractor's
    obligations as set forth in subparagraph
    \ref{terms:requirements-and-obligations} above. It is understood,
    however, that until the requirements of subparagraph
    \ref{terms:requirements-and-obligations} are fulfilled, final
    settlement will be withheld, and the forty-five (45) day payment
    provision will not apply.

    The parties have executed two copies of this Agreement effective as of
    the date first above written. The Carrier shall retain the original of
    this Agreement. One copy shall remain with the vehicle during the
    period of this Agreement, and the other copy shall be retained by the
    Contractor. When this Agreement covers more than one vehicle, the
    copies remaining with the vehicle may be photocopies if the original.

    The Contractor represents and warrants that the Contractor has read
    this Agreement in full, is familiar with its terms and provisions, and
    that no representations have been made either to or by the Carrier,
    either directly or indirectly, that are not incorporated herein.
    
    \subimport{.}{parties.tex}
}