\underline{Contractor Payments and Settlements}
\begin{enumerate}[ 
    ref = \SecondLevelEnumerator
]
    \item The Carrier, for the full and proper performance of this
    Agreement by the Contractor, agrees to pay the Contractor
    {\bfseries \GrossRevenueCommision} of the gross line haul revenue for
    the lease of the Contractor's Equipment. The gross line haul revenue
    shall be the gross revenue calculated based on the individual customer
    rate agreements established and on file in the Carrier's office. The
    gross line haul revenue shall not include any charges, fees, and costs
    intended to reimburse the Carrier. Exceptions will be made only as
    agreed upon in advance of any trip to which such an exception will
    apply. In the event of exceptions, the Carrier's documentation of
    exception pay will prevail.

    \item In the event that Contractor fails to expeditiously and safely
    deliver the commodities for any reason, Carrier reserves the right to
    deny payment of settlement for that shipment to Contractor.

    \item The Contractor shall be solely responsible for any and all costs
    of fuel necessary for the transportation of any freight dispatched by
    the Carrier. Contractor understands and agrees that any and all
    advances of money made by the Carrier to Contractor or its drivers for
    Contractor's fuel expenses will be deducted by the Carrier from the
    Contractor's settlements, and if not deducted, Contractor agrees to
    reimburse Carrier for the same.

    \item The Contractor shall not be entitled for additional compensation
    for loading and unloading beyond the contract settlement of
    {\bfseries \GrossRevenueCommision} of gross line haul revenue. The
    Contractor shall be solely responsible for any and all lumper fees
    incurred in the transportation of freight dispatched by the Carrier. In
    the event that a broker, or shipper agrees to cover such lumper fees,
    Contractor shall include a Comcheck confirmation number on the lumper
    receipt. The Contractor's settlement will be subject to change back by
    the Carrier if a broker and/or shipper does not cover lumper fees.

    \item The Contractor or its drivers shall not request or receive any
    advance of money directly from a broker or any other third party.
    Carrier shall have the sole discretion as to the advance of money to
    Contractor or its drivers, with the right to deduct the same from
    Contractor's settlement. Advances may be made to Contractor's drivers
    by Carrier unless Contractor, by a signed addendum to this Agreement,
    directs that there shall be no advances. Contractor hereby acknowledges
    that each advance of money made by the Carrier to the Contractor, or
    its drivers, is subject to an administrative fee of
    {\bfseries \CashAdvanceServiceFee} of the total advance, which shall be
    deducted by the Carrier from Contractor's settlement.

    \item Carrier shall make contract payments to Contractor upon
    submission by Contractor to Carrier, by US mail, express courier, or in
    person, of all of the following documentation:
    \begin{enumerate}[
        ref = \ThirdLevelEnumerator
    ]
        \item The log books required by the DOT.
        
        \item Those fully executed original documents necessary for Carrier
        to secure payment on the shipment, which consists of delivery
        receipts, receipted bills of lading or loading manifests, trip fuel
        reports, fuel receipts, monthly maintenance reports, and weight
        tickets where required, all of which must be properly completed and
        signed by the appropriate representatives of the consignor and
        consignee.
        
        \item Upon termination of this Agreement, and as a condition
        precedent to settlement, Contractor shall remove all identification
        devices of Carrier and, except in the case of identification
        painted directly on the equipment, return them to Carrier, pursuant
        to paragraph
        %\hyperref[sec:1--d]{1--d}
        of this Agreement.
    \end{enumerate}

    \item The Contractor understands and agrees that failure to submit all
    required documents will result in a delay or non-payment of settlement
    by Carrier.

    \item The Contractor shall legibly identify the Carrier's name, trip
    number obtained from dispatch, name, and signature of the Contractor or
    Contractor's driver, on the bill of lading. The Contractor understands
    and agrees that failure to include any piece of this information on the
    bill of lading will result in non-payment of settlement by Carrier.
    Contractor shall be responsible for inspecting the freight with the
    consignee, marking any exceptions to the condition or damage to the
    shipment that occurred during transit, and obtaining the receiver's
    signature upon delivery and acceptance of freight. Any notation of
    missing or damaged cargo on the bill of lading will result in a delay
    or non-payment of settlement by Carrier.

    \item The Contractor is prohibited from showing any bill of lading for
    freight dispatched by Carrier to any third party. The Contractor will
    be subject to an administrative fine of up to two thousand dollars
    (\$2,000.00) for each instance that this provision is violated.

    \item The Contractor shall not hold hostage any cargo dispatched by
    Carrier subject to payment of any prior settlement(s) Contractor
    believes is due from Carrier. The Contractor will be subject to an
    administrative fine of up to two thousand dollars (\$2,000.00) for each
    instance that this provision is violated.

    \item Where settlement payments are based on the percentage of gross
    line haul revenue for a shipment, Carrier shall provide information
    disclosing the rated freight bill amount to Contractor, subject to the
    right of Carrier to delete the names of shippers and customers, and
    Contractor shall have the right to examine copies of Carrier's
    applicable rate agreement at Carrier's office.

    \item Carrier may deduct from any amounts due to Contractor all amounts
    to cover Contractor's obligations under this Agreement, including any
    obligations of Contractor to Carrier for costs and expenses of
    Contractor incurred by Carrier, any amounts deducted by the broker
    and/or shipper from Carrier's gross line haul revenue for any reason,
    and all amounts which may have been advanced by Carrier on behalf of
    Contractor, plus those fines, penalties, interest, taxes, fees and
    assessments levied on the Contractor will, upon request, be provided by
    Carrier those documents necessary to determine and compute such charges
    and deductions.
\end{enumerate}