\underline{Equipment}. Contractor agrees and warrants:
\begin{enumerate}[
    ref = \SecondLevelEnumerator
]
    \item To furnish the equipment (``Equipment'') identified in the
    Equipment Description section herein. Contractor's Equipment list may
    be amended by an amendment signed by authorized representatives of
    Carrier and Contractor with copies provided to each.

    \item That equipment subject to this Agreement meets the US Department
    of Transportation (``DOT'') safety requirements and standards. Carrier
    reserves the right to terminate this Agreement at any time that
    Equipment subject to this Agreement fails to meet DOT safety
    requirements and standards.

    \item That Contractor holds full legal title or has the legal right to
    exercise full control over the Equipment.

    \item To affix to the Equipment the identification provided by Carrier
    required by federal, state, and other agencies, including Carrier's
    name and MC number. Such identification shall be removed immediately
    and returned to Carrier upon termination of this Agreement. In the
    event such identification cannot be removed but has to be painted over,
    Contractor shall immediately cause to have such repainting done and
    shall provide Carrier with a photograph of each repainted door, and in
    each photograph the front page of a current newspaper evidencing the
    date of the photograph. Failure to furnish evidence of the removal of
    identification from the equipment will result in the withholding of the
    final settlement.

    \item To pay all operating expenses, including, but not limited to, all
    expenses of fuel (including reefer fuel), oil, tires, maintenance,
    repairs, and other items necessary for the safe and efficient operation
    of the Equipment, meals and lodging, installation and usage fees of any
    and all communication equipment, such as Qualcomm or Citizens' Band
    (CB) radio on the Equipment, road taxes, mileage taxes, tolls, ferries,
    fines for parking, moving or weight violations, licenses, permits, or
    any other assessments based upon the operation of the Equipment in
    compliance with the rules and regulations of the DOT and all other
    federal, state, and foreign regulatory bodies having jurisdiction over
    Contractor's operations and Equipment, including all such costs related
    to all loaded and empty mileage. Contractor hereby agrees that, if it
    becomes necessary for Carrier to pay for any of Contractor's operating
    expenses, Carrier shall deduct such cost from Contractor's payment upon
    settlement.
    
    \item To maintain the Equipment in proper operating condition to
    satisfy any federal, state, or Carrier safety inspection at any time
    and to make such repairs as may be found necessary. The Contractor
    shall be responsible for undertaking and passing annual DOT safety
    inspections. The Contractor shall cause all vehicles to be in
    compliance with any and all applicable federal and state regulations as
    presently in force or enacted in the future and cause all vehicles to
    be operated in compliance therewith. The choice of location and persons
    to perform any necessary maintenance or repairs is vested exclusively
    in the Contractor. Contractor shall provide Carrier with legible copies
    of all repairs and maintenance performed on the Equipment at the time
    such work records covering the Equipment required by the regulations of
    the DOT and any other applicable governmental agency shall be forwarded
    by Contractor to Carrier by the last day of each calendar month during
    the term of this Agreement. If such records are not delivered to the
    Carrier within 7 days following the end of each month, or are
    incomplete, Carrier reserves the right to terminate this Agreement or
    suspend the same until complete records are supplied. Contractor
    further agrees that Carrier will have no obligation or responsibility
    for the repair of damage to the Equipment, regardless of cause.

    \item To ensure that any and all reefer trailers (``Reefer Equipment'')
    subject to this Agreement are calibrated every 3 months. The Contractor
    hereby agrees to operate such Reefer Equipment under ``continuous
    operation'' setting at all times while transporting freight dispatched
    by Carrier. For any and all produce shipments, Contractor shall use a
    temperature recorder to create a continuous temperature record and to
    ensure the constant setting of the set temperature. Unless said
    temperature recorder has been provided by the shipper, Contractor shall
    be responsible for the cost and maintenance of such temperature
    recorder.

    \item To conduct a ``Clean Operation'' in compliance with Carrier
    demands. Clean Operation shall include: all items required under safety
    procedures, check calls, on-time loading, on-time delivery, deliveries
    at correct destinations, prompt reporting of all cargo discrepancies,
    proper disposition of refused freight as directed by Carrier, no
    unauthorized handling of freight, no adverse safety reports, and no
    discourteousness while under dispatch or at Carrier facility. Carrier
    shall have the right to terminate this Agreement for cause, immediately
    and without prior notice, upon the occasion of any failure to comply
    herewith.

    \item The Contractor is responsible for ensuring seal integrity prior
    to the departure of a shipment and throughout delivery until the entire
    shipment has been delivered. Contractor is also responsible for keeping
    a continuous seal record, which shall be maintained and documented on
    all bills of lading for each stop of the shipment. Incidents where
    tampering may have compromised the integrity of a seal prior to
    delivery shall be reported to the Carrier immediately. Contractor shall
    not break or otherwise tamper with a seal, until and unless the
    receiver accepts the cargo and signs off on the bill of lading and
    directs the Contractor to break the seal. In the event that the
    Contractor breaks or tampers with a seal, or otherwise fails to ensure
    seal integrity at any point prior to delivery, the Carrier shall deem
    such shipment rejected by the receiver and reserves the right to deny
    payment of the settlement to the Contractor.

    \item That in the event the Carrier supplies the trailer to be pulled
    by the Contractor, the Carrier will maintain or cause to be maintained
    the trailer and accessory trailer equipment furnished by the Carrier.
    The Contractor shall be responsible and liable for all loss of or
    damage to any such trailer and accessory equipment occurring while in
    the possession or custody of the Contractor, arising out of the
    negligent or intentional acts of Contractor or Contractor's employees
    or agents, excepting such loss or damage as Carrier is compensated for
    under any applicable insurance or otherwise, and Contractor will
    indemnify and defend Carrier against any loss on account thereof. In
    the event Contractor supplies the trailer equipment under this
    Agreement, Contractor shall be responsible for the maintenance of the
    trailer and accessory equipment furnished by Contractor.
\end{enumerate}