\underline{Fines and Assessments}
\begin{enumerate}
    \item Contractor shall be financially responsible for any fines,
    violation, inspection or traffic citations, or other assessments
    arising form operation of the Equipment, including all penalties,
    tolls, ferry costs, detention and accessorial taxes, and other
    obligations that are incurred by reason of the route over which
    Contractor's vehicle is operated or the operation of same. The
    Contractor shall disclose to Carrier by fax or mail within 24 hours,
    receipt of any fine, violation, inspection or traffic citations or
    other assessment arising from operation of the Equipment. The
    Contractor shall keep a record of the confirmation of the fax or mail
    transmission to the Carrier showing date, time and fax numbers from/to
    which fax was transmitted.

    \item The Contractor is responsible for ensuring that each load is
    legal from all standpoints, including those of weight and size, before
    commencing each trip and during the conduct thereof. The Contractor
    shall notify Carrier regarding any cargo irregularities before pick-up
    is completed. If Contractor fails to ensure, or transports without the
    express written approval of the Carrier to exceed a limitation brought
    to the attention of the Carrier by Contractor, Contractor shall be
    responsible for any subsequent fines.

    \item The Contractor shall be responsible for ensuring that each driver
    operates in legal and safe manner. The Contractor shall be responsible
    for any fines levied for failure of any driver to so operate.
\end{enumerate}