\underline{Insurance and Claims}
\begin{enumerate}[
    ref = \SecondLevelEnumerator
]
    \item The Contractor shall be solely responsible for paying any and all
    insurance costs for the operation of the Contractor's Equipment subject
    to this Agreement. The Contractor agrees to provide, during the term of
    this Agreement, insurance naming the Carrier as additional insured on a
    per-occurrence basis, for the following coverage:
    \begin{enumerate}[
        ref = \ThirdLevelEnumerator
    ]
        \item Liability Insurance. The Contractor is responsible for
        providing primary liability insurance coverage on the Contractor's
        Equipment with minimum coverage limits of not less than
        \$750,000.00 combined single limit, excluding cargo insurance.

        \item Physical Damage. The Contractor is responsible for providing
        collision, fire, and theft insurance (physical damage) coverage on
        the Contractor's Equipment. When the Contractor's tractor is used
        to pull a trailer owned or operated by the Carrier, the Contractor
        shall be strictly liable to the Carrier for any loss or damage to
        said trailer, including the refrigeration unit, tires, and all
        other components, for each accident. An accident shall include
        damage to the Carrier's trailer caused by a preventable or
        non-recoverable collision or incident involving the Carrier's
        trailer while in the care and custody of the Contractor. The
        Contractor further agrees to be responsible and liable to the
        Carrier for the full amount of loss or damage to the Carrier's
        trailer while in the care and custody of the Contractor when said
        loss or damage results from illegal use or willful negligence or
        misconduct of the Contractor or the Contractor's employee.

        \item Cargo Insurance. The Contractor is responsible for providing
        cargo insurance coverage with minimum coverage limits of not less
        than \$200,000.00 per occurrence. The Contractor shall be
        responsible for any and all cargo claims that are a result of
        mechanical failure.

        \item The Contractor agrees to furnish to the Carrier proper
        evidence of each insurance coverage identified herein at the time
        of the execution of this Agreement and to maintain all such
        insurance in force at all times during the duration of this
        Agreement.

        \item The Contractor agrees to provide the Carrier written notice,
        within 24 hours, of cancellation or reduction of limits of
        insurance identified herein. Any such cancellation or reduction
        shall not affect the obligations of the Contractor to maintain such
        insurance.
    \end{enumerate}

    \item Pursuant to FHWA regulations under 49 USC 10927 and other
    applicable federal and state regulations, the Carrier shall maintain
    insurance coverage or provide evidence of self-insurance for public
    liability and property damage.

    \item In the event of any loss, damage, occurrence, or claim arising
    from the Contractor's performance of this Agreement, insurance policies
    provided by the Contractor under this Agreement shall provide primary
    coverage for such loss, damage, occurrence, or claim. Coverage by
    insurance policies maintained by the Carrier shall provide excess
    coverage, but not until and unless the limits of the Contractor's
    primary policies have been exhausted by the way of judgment or
    settlement.

    \item In the event that collection of transportation charges prior to
    delivery is required, the Contractor will collect and promptly remit to
    the Carrier all amounts paid to the Contractor or the Contractor's
    drivers by the Carrier's consignors or consignees for transportation
    charges or otherwise under the Carrier's shipping or billing documents.
    The Contractor will be liable for any amounts which the Contractor
    fails to collect when so specified on the shipping or billing documents
    unless an officer or authorized employee of the Carrier gives the
    Contractor written permission to deliver such shipment without the
    collection of said charges.
\end{enumerate}