\newcommand{\PhysicalQualificationsAndExaminationsFootnote}{%
    \textbf{The Office of the Federal Register}:
    \textsl{Title 49 -- Part 391: Subpart E --- Physical Qualifications
    and Examinations} \\
    \href
        {https://www.ecfr.gov/current/title-49/part-391/subpart-E}
        {https://www.ecfr.gov/current/title-49/part-391/subpart-E}
}

\underline{Contractor's Personnel}
\begin{enumerate}
    \item Contractor agrees to furnish drivers and all other necessary
    labor to perform all of the work Carrier provides for in its rate
    schedules and contracts necessary for:
    \begin{enumerate}
        \item The transportation of such commodities
        
        \item The loading and unloading of such commodities
    \end{enumerate}

    \item Contractor certifies, represents, and warrants that all driver
    personnel furnished by Contractor and covered by this Agreement will
    meet and satisfy the driver qualifications of the DOT, the appropriate
    states, and those of Carrier based thereon and related thereto. This
    includes all applicable drug and alcohol regulations, and warrants
    cooperation with all testing procedures. Only such qualified personnel
    may operate the Equipment leased to Carrier by the Contractor under
    this Agreement. The Contractor shall furnish to Carrier proof of such
    qualifications as Carrier may reasonably require.

    \item Contractor agrees that Contractor and Contractor's drivers,
    personnel, and agents will not place in or on, or carry onto the
    Equipment, any alcohol, narcotics, illegal drugs, controlled
    substances, explosives, firearms, contraband, or unauthorized
    commodities or hazardous materials. Any violation of this provision
    shall permit Carrier to terminate this Agreement immediately without
    notice. If a violation of this provision subjects Carrier to any
    expenditures or sanctions, Contractor agrees to reimburse Carrier for
    the same.

    \item The Contractor and all personnel furnished or used by the
    Contractor, including drivers, driver's helpers, and laborers, are the
    employees, agents, or independent contractors of the Contractor and not
    of Carrier and as such, Contractor is solely responsible for:
    \begin{enumerate}
        \item The employee deductions, as may be required by governmental
        agencies.
        
        \item Self-employment taxes, withholding taxes, FICA taxes,
        unemployment compensation taxes, and any other such taxes or
        obligations.

        \item Providing workers' compensation insurance and occupational
        accident and disability for any and all personnel and drivers
        furnished by the Contractor and including the Contractor, who are
        qualified to operate the Equipment.

        \item The direction and control of the Contractor's employees,
        agents, and independent contractors, including selecting, hiring,
        firing, supervising, directing, training, setting wages, hours and
        working conditions, and paying and adjusting grievances of the
        Contractor's directing, training, setting wages, hours and working
        conditions, and paying and adjusting Contractor's employees,
        agents, and independent contractors,

        \item educating Contractor's employees, agents, and independent
        contractors regarding Carrier's policies, requirements, and terms
        of this Agreement,

        \item any and all costs associated with commercial driver physical
        qualification test mandated under 49 {\S\S} CFR 391.41 -- 391.49%
        \footnote{\PhysicalQualificationsAndExaminationsFootnote} or
        any other qualification testing conducted by the Contractor, and

        \item any and all operating costs and expenses incurred by any of
        the Contractor's employees, agents, and independent contractors
        during the operation of the Equipment subject to this Agreement.
    \end{enumerate}
\end{enumerate}