\begin{enumerate}
    \item \textbf{Fees and Payment Methods.} All fees are provided for in the
    fee table. As provided in 62 O.S. ยง41.5(q), the SOS is authorized to charge
    a convenience fee for any electronic/on-line transaction. A convenience fee
    of 4\% will be charged for all payments by credit card, 18 O.S. ยง1142(G)(2).
    The SOS accepts Discover, MasterCard and Visa online.

    \item \textbf{Hours of Operation.} This Site is normally available 24 hours
    a day Monday through Saturday. Due to system maintenance requirements,
    availability of the Site on Sundays will be from 6:00 am to midnight
    (Central Time).

    \item \textbf{User Information.} The Web Site's service application uses
    session and persistent cookies to authenticate and facilitate user logins.
    The User's name, email, phone, and fax number are stored for a period of 30
    days, allowing re-entry to the Site without entering login data. If you do
    not wish for this information to be stored on your hard drive you may
    disable the use of cookies from your browser. This feature is usually found
    in the Security or Preference settings of your browser. It is the obligation
    of the User to disable this function.

    \item \textbf{Violation of the Oklahoma Computer Crimes Act (21 O.S. ยง1951
    et. seq.).} Security measures are in place to protect the loss, misuse and
    alteration of the information/data within this Site. It is a misdemeanor
    punishable by a fine of not more than Five Thousand Dollars (\$5,000.00), or
    by imprisonment in the county jail not to exceed thirty (30) days, or by
    both such fine and imprisonment to willfully and without authorization, gain
    or attempt to gain access to a computer, computer system, computer network
    or any other property, or to use or cause to be used computer services. It
    is a felony punishable by a fine of not less than Five Thousand Dollars
    (\$5,000) and not more than One Hundred Thousand Dollars (\$100,000.00), or
    by confinement in the State Penitentiary for a term of not more than ten
    (10) years, or by both such fine and imprisonment to willfully, and without
    authorization, gain or attempt to gain access to and damage, modify, alter,
    delete, destroy, copy, make use of, disclose or take possession of a
    computer, computer system, computer network or any other property. By
    accepting the terms of this agreement, the user agrees to indemnify the
    state for any loss caused by conduct of the User or an employee or agent of
    the User that amounts to a violation of the Oklahoma Computer Crimes Act.

    \item \textbf{Right to Change the Site.} The SOS reserves the right to
    discontinue, edit, delete, restrict or change any aspect of the Site at the
    SOS's sole discretion and without prior notice or liability. Such changes
    may include, but are not limited to: (i) access availability times, (ii)
    compatibility with certain computer software or hardware, and (iii) amounts
    of use time permitted.

    \item \textbf{Entire Agreement.} User agrees that the Terms and Conditions
    of Use Agreement (``Agreement'') constitutes the entire agreement between
    the user and the SOS with respect to the use of the Site, and supersedes all
    previous and contemporaneous agreements, representations, warranties and
    understandings, written or oral, between the user and the SOS with respect
    to the Site. Any modifications to the provisions contained within this
    agreement must be in writing and signed by the Secretary of State.
    
    \item \textbf{Copyrights and Public Information.} The content organization,
    graphics, design, computer code, compilation and other materials on or
    related to the Site are protected under applicable copyright, trademark and
    other proprietary and intellectual property rights of their respective
    owners. The SOS places no restriction on the data that constitutes
    information in the public domain, however, certain information and names
    contained in the data may be owned by third parties and protected under
    applicable copyright, trademark and other proprietary and intellectual
    property rights of those third parties. User does not acquire ownership
    rights to any content, document or other materials viewed through the Site
    or obtained from the Site. User agrees not to violate any of the applicable
    intellectual property rights of third parties or to facilitate such
    infringement by any means.

    \item \textbf{Limited Right to Use.} Any content, graphic, form or document
    viewed, printed, downloaded from this Site is for the personal use of the
    User and is not for republication, distribution, assignment, sublicense,
    sale, preparation of derivative works or other use. No part of any content,
    graphic, form or document may be reproduced in any form or incorporated into
    any information retrieval system, electronic or mechanical, other than for
    personal use. All copyright and other proprietary notices must be kept
    intact.

    \item \textbf{Prohibited Behavior.} User is prohibited from using the Site
    in any way to:
    i) restrict or inhibit another user from using and enjoying the Site;
    ii) post or transmit any unlawful, threatening, abusive, libelous,
    defamatory, obscene, vulgar, pornographic, profane or indecent information
    of any kind, including without limitation any transmissions constituting or
    encouraging conduct that would constitute a criminal offense, give rise to
    civil liability or otherwise violate any local, state, national or
    international law;
    iii) post or transmit comments containing harassing or offensive language,
    including sexual references, sexual nicknames, racial slurs or rude or
    deliberately offensive comments or engage in disruptive activities online,
    including excessive use of scripts, sound waves, scrolling (repeating the
    same message over and over), or use viruses, robots, worms or trojan horses;
    iv) access another person's or entity's, account information or briefcase
    files without the permission of that person or entity;
    v) post or transmit any information, software or other material which
    violates or infringes the rights of others, including material which is an
    invasion of privacy or publicity rights or which is protected by copyright,
    trademark or other proprietary right without first obtaining permission from
    the owner or right holder;
    vi) upload, post or otherwise transmit any information, software or other
    material that contains a virus, worm, time bomb, trap door, or any other
    harmful component that is designed to interrupt, destroy, impair or limit
    the functionality, or interfere in the performance of the products and
    services of the SOS;
    vii) post or transmit content that encourages or provides instructional
    activities about illegal activities, such as hacking;
    viii) post, transmit or in any way exploit any information, software or
    other material for advertising or commercial purposes;
    ix) solicit other users to join, become members of, or contribute money to
    any online service or other organization, advocate or attempt to get users
    to join in legal or illegal schemes or plan or participate in scams
    involving other users;
    x) impersonate any person or entity or falsely state or otherwise
    misrepresent your professional or other affiliation with any person or
    entity including, but not limited to an SOS official or employee;
    xi) decompile, disassemble, modify, translate, adapt, reverse engineer,
    create derivative works from, or sublicense any proprietary software
    deployed in connection with SOS products and services;
    xii) use the Site to collect personally identifying information about users
    of the Site in violation of the SOS's Privacy Policy; or xiii) perform any
    activities that the SOS determines (in its sole discretion) may be harmful
    to SOS, the Site or other users of the Site.
    
    \item \textbf{No Unlawful Purposes.} User agrees that neither the Site nor
    any information or services related thereto will be used for any unlawful
    purpose. It is a felony punishable by imprisonment in the State Penitentiary
    for a term of not more than five (5) years, or by a fine of not more than
    Five Thousand Dollars (\$5,000.00), or by both to communicate with, store
    data in, or retrieve data from a computer system or computer network for the
    purpose of using such access to violate any of the provisions of the
    Oklahoma Statutes.

    \item \textbf{False Documents.} It is a felony under 21 O.S. ยง463 to
    knowingly offer a false or forged instrument to be filed, registered, or
    recorded in any public office within the State of Oklahoma.

    \item \textbf{Monitoring.} User agrees and understands that the SOS has no obligation
    to monitor the Site. The SOS reserves the right to disclose information as
    necessary to satisfy any law, regulation or governmental request, to refuse
    to post or to remove information or materials, in whole or in part, that in
    the SOS's sole and absolute discretion are objectionable or in violation of
    this Agreement. User acknowledges that the SOS reserves the right to monitor
    any and all information transmitted or received through the Site, for
    operational and other purposes. Use of the Site constitutes consent to such
    monitoring. Business \& Commerce Code, section 36.27, provides that a person
    commits an offense if the person knowingly or intentionally signs and
    presents for filing or causes to be presented for filing an assumed name
    document that: (1) indicates that the person signing the document has the
    authority to act on behalf of the entity for which the document is presented
    and the person does not have that authority; (2) contains a material false
    statement; or (3) is forged. The offense is punishable as if it were an
    offense under the Oklahoma Penal Code, section 37.10 (tampering with a
    governmental record).

    \item \textbf{Indemnification.} User agrees to defend, indemnify and hold
    harmless the SOS, the State of Oklahoma, their affiliates and their
    respective, officers, employees and agents from and against any and all
    claims, actions, suits or proceedings, as well as any and all losses,
    liabilities, damages, costs and expenses (including reasonable attorneys
    fees) arising out of or related to (a) any material posted or otherwise
    provided by user that infringes any copyright, trademark, trade secret,
    patent or other intellectual property right of any person or defames any
    person or violates their rights of publicity or privacy, (b) any
    misrepresentation made by user in connection with use of the Site; (c) any
    violation by user of this Agreement; and (d) any claims brought by other
    persons or entities arising from or related to use of the Site, including
    information obtained through the Site. It is agreed that the User assumes
    all risks of whatever kind or nature for or arising from use of the Site and
    the SOS, the State of Oklahoma, and their affiliates disclaim any liability
    whatsoever for use of the Site by the User.

    \item \textbf{Infringement Policy.} The SOS respects the intellectual
    property of others, and asks all Users to do the same. The SOS reserves the
    right to terminate use of the Site if it determines in its sole and absolute
    discretion that the User is involved in infringing activity, including
    alleged acts of first-time or repeat infringement, regardless of whether the
    activity is ultimately determined to be infringing.

    \item \textbf{Miscellaneous.} This Agreement shall be treated as executed
    and performed in Oklahoma City, Oklahoma County, Oklahoma and shall be
    governed by and construed in accordance with the laws of the State of
    Oklahoma (without regard to conflict of law principles). The language in
    this Agreement shall be interpreted as to its fair meaning and not strictly
    for or against either party. All legal proceedings arising out of or in
    connection with this Agreement shall be brought solely in Oklahoma County,
    Oklahoma. User expressly submits to the exclusive jurisdiction and venue of
    said courts and consents to extra-territorial service of process. Should any
    part of this Agreement be held invalid or unenforceable, that portion shall
    be construed as consistent with the applicable law and the remaining
    portions shall remain in full force and effect. To the extent that anything
    in or associated with the Site is in conflict or inconsistent with this
    Agreement, this Agreement shall take precedence. The SOS's delay or failure
    to enforce any provision of this Agreement shall not be deemed a waiver of
    such provision nor of the right to enforce such provision. No waiver by
    either party of any breach or default hereunder shall be deemed a waiver of
    any subsequent breach or default. The titles and subtitles used in this
    Agreement are used for convenience only and are not to be considered in
    construing or interpreting this Agreement.
\end{enumerate}